\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-24 paper/algorithm.tex
paper: working on optimality proof

\begin{definition}
We say that a plan $p$ with cost $\langle l, t \rangle$ dominates a plan $p'$ with cost $\langle l', t' \rangle$ if $l < l'$ and $t < t'$. We denote this as $\doms{p}{p'}$. 
\end{definition}

@@

>>>>

\begin{definition}
We say that a plan $p$ with cost $\langle l, t \rangle$ dominates a plan $p'$ with cost $\langle l', t' \rangle$ if $(l \leq l' \land t < t') \lor (l < l' \land t \leq t')$. We denote this as $\doms{p}{p'}$. 
\end{definition}

@@

\subsection{Optimality}
We prove the optimality of the final plan selected by showing that our cost-model and algorithm
construct a complete Pareto frontier.

%\begin{definition}
%Given two plans $p$ and $p'$,  such that $|\textsc{Dirty}(p) \setminus \textsc{Dirty}(p')| = n$, and $\textsc{Time}(p) \leq \textsc{Time}(p')$,
%we say $p$ yields $p'$ with dirty set size reduction $n$, if we can add any number of imputation and relational operators to $p$ to obtain
%$p'$. We denote this $p \xrightarrow{n} p'$. 
%\end{definition}

\todo{define F and way its ok, why it depends solely on the dirty set... the algorithm keeps all other state relevant, so this is all thats needed for transformations}

\begin{theorem}
Our cost-model and plan-cache semantics results in a final set of plans that constitute a Pareto frontier.
\end{theorem}

\begin{proof}
For contradiction, let $p_1$ and $p_2$ be plans such that $\doms{p_1}{p_2}$. Given a function $F: D \rightarrow O$ (d is dirty sets, o is operators),
assume plans only $p_3 \in F(\textsc{Dirty}(p_2))(p_2)$, and $p_4 \in F(\textsc{Dirty}(p_1))(p_1)$, and that $\dom{p_3}{p_4}$.

A contradiction arises from in one of two cases

case 1: p1 doesn't dominate p2 (that con only happen if the dirty sets are different) (they are comparable), so not tossed
case 2: they have the same dirty set, and since dirty set determines F exclusively, then p3 and p4 are reachable for both, so they are substituable
\end{proof}

%\begin{proof}
%We prove this by induction on the reduction in the size of the dirty set for a plan.
%
%For the base case, given a plan $p$, we obtain $P_1 = \{ p' | p \xrightarrow{1} p'  \}$. We construct a set of plans for each
%dirty set by keeping all non-dominated plans with the same dirty set. By definition, each of these sets are a Pareto frontier 
%to reduce $\textsc{Dirty}(p)$ by 1.
%
%By the induction hypothesis, we can do the same on $P_n = \{ p' | p \xrightarrow{n} p' \}$ to produce a set of Pareto frontiers to
%reduce $\textsc{Dirty}(p)$ by $n$.
%
%Given a Pareto optimal plan in our search space $p''$ s.t. $p \xrightarrow{n+1} p''$, it must be the case that there exists a plan $p''_{prev}  \xrightarrow{1} p''$. 
%
%If $p''_{prev}$ is Pareto optimal for its dirty set and a reduction of size $n$, then we can directly yield $p''$ from the appropriate
%frontier.
%
%If $p''_{prev}$ is not Pareto optimal, there exists a Pareto optimal plan $\widehat{p''_{prev}}$ with the same dirty set
%as $p''_{prev}$, which dominates it, so we can apply the same imputation operations to $\widehat{p''_{prev}}$ to yield $p''$.
%\end{proof}
%
%\todo{We're working on a proof of optimality for the final set of plans created}
